The Mass Distribution of Stellar-Mass Black Holes

### 2010-10-20 paper.tex
First stab at introduction.

>>>>

(X-Ray binaries are important---supernova, evolutionary processes, GW,
etc.)

\citet{Bailyn1998} examined a sample of seven transient X-ray binaries
thought to contain a black hole, concluding in a Bayesian analysis
that the mass function was strongly peaked around seven solar masses.
They found strong evidence for a ``gap'' between the least massive
black hole and the upper limit for neutron star masses of 3 $\Msun$.

A more recent study \citep{Ozel2010}, also in a Bayesian framework,
largely confirmed these findings, examining 16 low-mass X-ray binary
systems containing black holes and finding a strongly peaked
distribution at $7.8 \pm 1.2 \, \Msun$.  \citet{Ozel2010} used two
models for the mass function: a Gaussian and a decaying exponential
with a minimum ``turn-on'' mass (motivated by the analytical model of
the black-hole mass function in \citet{Fryer2001}), finding in both
cases strong evidence of a mass gap.  They argue that this mass gap
cannot be explained by observational selection effects.

In this work, we use observations of 20 low- and higher-mass galactic
X-ray binaries that contain black holes to constrain the mass function
for stellar mass black holes in the galaxy.  We consider separately
the 15 low-mass X-ray binaries containing Roche-lobe-filling
secondaries with masses smaller than the black hole primary, and a
complete sample including these systems and five higher-mass, wind-fed
systems where the secondary is heavier than the black hole primary.

We use a Bayesian Markov-Chain Monte Carlo analysis to explore various
models for the black hole mass function for both samples, including
those of \citet{Ozel2010} and \citet{Bailyn1998}.  We include both
parameteric models, such as a Gaussian, and non-parameteric models
where the mass function is represented by histograms with various
numbers of bins.  After computing posterior distributions for the
model parameters, we use model selection techniques (including a new
technique for efficient reversible-jump MCMC \citep{Farr2010}) to
compare the evidence for the various models from both samples.

We find, like \citet{Ozel2010} and \citet{Bailyn1998}, strong evidence
for a mass gap among the best models for both systems, with the best
model for the lower-mass systems giving a minimum black hole mass of
4.3 $\Msun$ (at 90\% confidence), and the best model for the combined
sample of lower- and high-mass systems giving a minimum black hole
mass of 4.5 $\Msun$ (at 90\% confidence).  Among the models with lower
evidence, most also have a mass gap.

The theoretical model from \citet{Fryer2001}, a decaying exponential,
considered for the low-mass systems in \citet{Ozel2010}, has
relatively low evidence.  We find that the lower-mass systems are best
described by a Gaussian (the other model from \citet{Ozel2010}).  We
find that the theoretical model from \citet{Fryer2001} is, however,
the preferred model for the combined sample, while a Gaussian has much
lower evidence in this case.  A model with two separate Gaussian peaks
also has high evidence for the combined sample of systems, suggesting
\fixme{differences in the distributions of lower- and high-mass X-ray
  binary systems}.

The structure of this paper is as follows \fixme{This will change
  dramatically}.
